### 2016-04-06 text/ms.Rmd
Mainly edits to the paper

We fit four individual data-limited models that use data on catch and basic
life history parameters to estimate $B/B_\mathrm{MSY}$. We chose these models
because TODO. Three of the models are mechanistic and based generally on
Schaefer biomass dynamics [@schaefer1954] of the form

@@

* *mPRM* (modified panel regression model) is a modified version of the
  panel-regression model from @costello2012. Unlike the other models, mPRM is
  empirical and not mechanistic --- it uses the RAM Legacy Stock Assessment
  database to fit a regression model to a series of characteristics of the
  catch time series and stock with stock-assessed $B/B_\mathrm{MSY}$ as the
  response. The model used in this paper is modified from the original --- it
  condenses the life-history categories into three categories to match the
  simulated dataset, removes the maximum catch predictor since the absolute
  catch in the simulated dataset is arbitrary, and does not implement the bias
  correction needed in @costello2012 since we do not derive estimates of
  median status across multiple stocks. <!--TODO is this last sentence
  necessary? -->

## Simulated data set to build the ensemble TODO: finish this

@@

@@

We compared an ensemble average and three superensembles of varying
complexity: a linear model with two-way interactions, a random forest, and
a boosted regression tree. We describe these models as estimating
$\hat{\theta}$, which represents either the ensemble estimated $\log
B/B_\mathrm{MSY}$ or slope of $B/B_\mathrm{MSY}$. The individual model
estimates of $\log B/B_\mathrm{MSY}$ or slope of $B/B_\mathrm{MSY}$ are
represented as $b$ for models $i$ $1$ through $n$ ($4$). The ensemble average
was calculated as:

\begin{equation}
\hat{\theta} = \frac{1}{n} \sum_{i=1}^n \hat{b_i}.
\end{equation}

$$ \hat{\theta} = \argmin_\theta \left( L(b \, | \, \hat{b}{\mathrm{ensemble}})
\right) $$ $$ \hat{b}\mathrm{ensemble} = f \left( \hat{b}\mathrm{CMSY}, \,
\hat{b}\mathrm{COM-SIR}, \, \hat{b}\mathrm{SSCOM}, \, \hat{b}\mathrm{mPRM}, \,
S(0.2), \, S(0.5), \, | \, \theta \right) $$

We fit the linear model superensemble with all second-order interactions:

\begin{equation} \theta_{\mathrm{ensemble}(i)} = \beta_0 + \sum_{j=1}^m \beta_j
\theta_{j(i)} + \sum_{j=1}^m \sum_{\substack{k =1 \ j \neq k}}^m \beta_{kj}
\theta_{k(i)} \theta_{j(i)} + \epsilon_i, \quad \epsilon_i \sim
\mathrm{Normal}(0, \sigma), \end{equation}

>>>>

We fit four individual data-limited models that use data on catch and basic
life-history parameters to estimate $B/B_\mathrm{MSY}$. We chose these models
because because they can be fit to the vast majority of fisheries around the
world, are established in the literature, and have been extensively simulation
tested [@rosenberg2014].

Three of the models are mechanistic and based generally on Schaefer biomass
dynamics [@schaefer1954] of the form

@@

* *mPRM* (modified panel regression model) is a modified version of the
  panel-regression model from @costello2012. Unlike the other models, mPRM is
  empirical and not mechanistic --- it uses the RAM Legacy Stock Assessment
  database to fit a regression model to a series of characteristics of the
  catch time series and stock with stock-assessed $B/B_\mathrm{MSY}$ as the
  response. The model used in this paper is modified from the original --- it
  condenses the life-history categories into three categories to match the
  simulated dataset, removes the maximum catch predictor since the absolute
  catch in the simulated dataset is arbitrary, and does not implement the bias
  correction needed in @costello2012 since we do not derive estimates of
  median status across multiple stocks.

## Simulated data set to build the ensemble

@@

We compared an ensemble average and three superensembles of varying
complexity: a linear model with two-way interactions, a random forest, and
a boosted regression tree. We describe these models as estimating
$\hat{\theta}$, which represents either the ensemble estimated $\log
B/B_\mathrm{MSY}$ or slope of $B/B_\mathrm{MSY}$. The individual model
estimates of $\log B/B_\mathrm{MSY}$ or slope of $B/B_\mathrm{MSY}$ are
represented as $b$ for models $i$ $1$ through $n$. The subscript $j$ indexes
the fisheries from $1$ through $m$. The ensemble average was calculated as:

\begin{equation}
\hat{\theta_j} = \frac{1}{n} \sum_{i=1}^n \hat{b}_{i,j} , \quad
\mathrm{for}\ j  =  1,...,m.
\end{equation}

\noindent We fit the linear model superensemble with all second-order
interactions:

\begin{equation}
\hat{\theta_j} = \beta_0 + \beta_1 \hat{b}_{j,0} + ... +
\beta_{1,2} \hat{b}_{j,1} \hat{b}_{j,2} + ... +
\epsilon_j,
\quad
\mathrm{Normal}(0, \sigma^2)
\quad \mathrm{for}\ j  =  1,...,m
\end{equation}

@@
